### 2020-03-31 ISSTA/implementation.tex
fix andrews ref

While the formal definitions above offer a framework for checking nondeterminism, they leave unspecified the key notions of \emph{state},
\emph{visible state}, and \emph{actions}.  For example, we could
identify the state and visible state of a system as identical with the
full set of memory locations accessed by that system, and actions with
processor instructions.  However, this
definition is highly impractical.  First, it is
extremely inefficient to compare multiple executions for
full-memory-state equivalence at every instruction step.  Second, and
even more importantly, as noted in the introduction, very few programs
are deterministic in this strict sense.  What is a practical level of granularity for (visible) states and actions that
can be efficiently checked, and matches (for the most part) developer
and tester intuitions about what should behave deterministically?
Andrews et al. formalized a value-pool-based model that is widely used in
tools, including Randoop \cite{Pacheco}, where
unit tests are \emph{canonically} given as:

>>>>

While the formal definitions above offer a framework for checking nondeterminism, they leave unspecified the key notions of \emph{state},
\emph{visible state}, and \emph{actions}.  For example, we could
identify the state and visible state of a system as identical with the
full set of memory locations accessed by that system, and actions with
processor instructions.  However, this
definition is highly impractical.  First, it is
extremely inefficient to compare multiple executions for
full-memory-state equivalence at every instruction step.  Second, and
even more importantly, as noted in the introduction, very few programs
are deterministic in this strict sense.  What is a practical level of granularity for (visible) states and actions that
can be efficiently checked, and matches (for the most part) developer
and tester intuitions about what should behave deterministically?
Andrews et al. formalized a value-pool-based model \cite{AndrewsTR} that is widely used in
tools, including Randoop \cite{Pacheco}, where
unit tests are \emph{canonically} given as:
